\textsf{Are large language models superhuman chemists?}

### 2024-03-26 src/tex/ms.tex
update authors and acknowledgements

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation and a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena.
We thank Stability.AI for the use of its HPC cluster and for its generous donations.
We also thank the OpenBioML.org community and their ChemNLP project team for useful discussions.

@@

M.R. and U.S.S. thanks the “Deutsche Forschungsgemeinschaft” for funding under the regime of the priority programme SPP 2363 “Utilization and Development of Machine Learning for Molecular Applications – Molecular Machine Learning” (SCHU 1229/63-1; project number 497115849).

The authors thank Julian Kimmig for feedback on the web app.

>>>>

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation, a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena and the FAIRmat consortium.
We also thank Stability.AI for the use of its HPC cluster and for its generous donations.
In addition, we thank the OpenBioML.org community and their ChemNLP project team for useful discussions. Moreover, we thank Pepe Márquez, and Santiago Miret for discussion and support and Julian Kimmig for feedback on the web app.

@@

M.R. and U.S.S. thanks the \enquote{Deutsche Forschungsgemeinschaft} for funding under the regime of the priority programme SPP 2363 \enquote{Utilization and Development of Machine Learning for Molecular Applications – Molecular Machine Learning} (SCHU 1229/63-1; project number 497115849).
